### 2019-04-17 report/MSc_Report.tex
Function update

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sat Apr 13 14:58:52 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lllrrrr}
  \hline
Study & Comparison\_type & Outcome & Events & Total & Events\_c & Total\_c \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11.00 & 41.00 & 11.00 & 41.00 \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14.00 & 27.00 & 13.00 & 26.00 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Example of two comparisons as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted} 
\label{barbiturate.row}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sat Apr 13 14:58:52 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Study & Comparison & Outcome \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
   \hline
\end{tabular}
\endgroup
\caption{Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given} 
\label{barbiturates}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sat Apr 13 14:58:53 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lr}
  \hline
  \hline
Missing mean values & 1287 \\ 
  Missing standard deviations & 999 \\ 
  Missing effects & 158 \\ 
  Missing study year & 27234 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number of missing variables and measurements in the dataset} 
\label{missing}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sat Apr 13 14:58:58 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
n & Cumulative sum (without subgroups) & Cumulative sum (with subgroups) \\ 
  \hline
1 & 109191 & 186300 \\ 
  2 & 67699 & 83956 \\ 
  3 & 47800 & 52270 \\ 
  4 & 36169 & 36198 \\ 
  5 & 28090 & 26570 \\ 
  6 & 22702 & 20126 \\ 
  7 & 18547 & 15896 \\ 
  8 & 15475 & 12935 \\ 
  9 & 13008 & 10821 \\ 
  10 & 11008 & 9229 \\ 
  11 & 9362 & 7991 \\ 
  12 & 8057 & 7070 \\ 
  13 & 6988 & 6368 \\ 
  14 & 6044 & 5783 \\ 
  15 & 5328 & 5328 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Cumulative number of groups with number of reproduction trials >= n} 
\label{repr.groups}
\end{table}

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}

@@

\vspace{0mm}
There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results. In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes. From 2312 meta-analyses with continouos outcomes, most meta-analyses with rejected null hypotheses have been found by the Thompson and Sharp test (0.319), followed closely by Eggers test (0.309) and Begg and Mazumdar's test (0.131).
The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 5717). The test that rejects most null hypotheses is here Egger's test (0.186), followed by R\"ucker's test (0.163), Harbord's test (0.144), Peters test (0.142) and Schwarzer's test (0.088).

@@

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sat Apr 13 14:59:07 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
 & Test Agreement & P-value Correlation \\ 
  \hline
egger.schwarzer & 0.83 & 0.38 \\ 
  egger.peter & 0.84 & 0.44 \\ 
  egger.rucker & 0.83 & 0.39 \\ 
  egger.harbord & 0.91 & 0.75 \\ 
  schwarzer.peter & 0.85 & 0.24 \\ 
  schwarzer.rucker & 0.83 & 0.30 \\ 
  schwarzer.harbord & 0.88 & 0.52 \\ 
  rucker.peter & 0.89 & 0.66 \\ 
  harbord.peter & 0.86 & 0.45 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)} 
\label{agreement.bin}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sat Apr 13 14:59:07 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
 & Test Agreement & P-value Correlation \\ 
  \hline
thomson.egger & 0.85 & 0.67 \\ 
  thomson.begg & 0.75 & 0.45 \\ 
  egger.begg & 0.75 & 0.38 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)} 
\label{agreement.cont}
\end{table}

\vspace{0mm}
Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies. The p-values of two tests are shown with respect to the sample size of the studies in Figure \ref{pvalues.samplesize.bin} for peters test based on dichotomous outcomes and in Figure \ref{pvalues.samplesize.cont} for thomson and sharp's test based on continuous outcomes. %(Suggests that 10 is likely too small)
A trend towards more significant p-values is visible for larger sample sizes.

@@

\end{knitrout}
\caption{P-values of peters test for small study effects and their corresponding sample size (dichotomous outcomes)}
\label{pvalues.samplesize.bin}
\end{figure}

@@

\end{knitrout}
\caption{P-values of thomson and sharp's test for small study effects and their corresponding sample size (continuous outcomes)}
\label{pvalues.samplesize.cont}
\end{figure}

\vspace{0mm}
One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects. The mean fraction of trimmed comparisons for binary outcomes is 0.17 and the median 0.15. A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes. In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses. In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes. In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.

@@

\end{knitrout}
\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
\label{trimfill.cont}
\end{figure}

The mean fraction of trimmed comparisons for continuous outcomes is 0.22 and the median 0.2.

The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

@@

\end{knitrout}
\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
\label{trimfill.bin}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}

@@

\subsection{Small Study Effect Correction}

Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.

% # <<results = 'asis', Echo = FALSE>>=
% # rejection.bin <- data.bin.ext %>% summarize(egger.rejection = mean(egger.test),
% #                                             schwarzer.rejection = mean(schwarzer.test),
% #                                             rucker.rejection = mean(rucker.test),
% #                                             harbord.rejection = mean(harbord.test),
% #                                             peter.rejection = mean(peter.test))
% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
% # @

>>>>

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Apr 16 13:54:44 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lllrrrr}
  \hline
Study & Comparison\_type & Outcome & Events & Total & Events\_c & Total\_c \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11.00 & 41.00 & 11.00 & 41.00 \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14.00 & 27.00 & 13.00 & 26.00 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Example of two comparisons as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted} 
\label{barbiturate.row}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Apr 16 13:54:44 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Study & Comparison & Outcome \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
   \hline
\end{tabular}
\endgroup
\caption{Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given} 
\label{barbiturates}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Apr 16 13:54:44 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lr}
  \hline
  \hline
Missing mean values & 1287 \\ 
  Missing standard deviations & 999 \\ 
  Missing effects & 158 \\ 
  Missing study year & 27234 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number of missing variables and measurements in the dataset} 
\label{missing}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Apr 16 13:54:49 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
n & Cumulative sum (without subgroups) & Cumulative sum (with subgroups) \\ 
  \hline
1 & 109191 & 186300 \\ 
  2 & 67699 & 83956 \\ 
  3 & 47800 & 52270 \\ 
  4 & 36169 & 36198 \\ 
  5 & 28090 & 26570 \\ 
  6 & 22702 & 20126 \\ 
  7 & 18547 & 15896 \\ 
  8 & 15475 & 12935 \\ 
  9 & 13008 & 10821 \\ 
  10 & 11008 & 9229 \\ 
  11 & 9362 & 7991 \\ 
  12 & 8057 & 7070 \\ 
  13 & 6988 & 6368 \\ 
  14 & 6044 & 5783 \\ 
  15 & 5328 & 5328 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Cumulative number of groups with number of reproduction trials >= n} 
\label{repr.groups}
\end{table}

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}

@@

It is also possible to look how the amount of meta-analysis with significant pooled effect size estimates changes over time, e.g. mean publication year (of studies included in the meta-analysis). 0.05 is used here as the threshold for $p$-value significance and subsequent null-hypothesis rejection. To constrict random fluctuation in the proportion, only mean publication years with a certain amount of meta-analyses are shown ($n < 180$). The $p$-value of the fixed effects meta analysis model is used to decide about rejection of the null-hypothesis. As Figure \ref{treatment.effect.significance.overtime} shows, the proportion of meta-analyses with significant treatment effect estimates stays roughly constant over time.

@@

\end{knitrout}
\caption{Proportion of significant treatment effect estimates over time (mean publication year).}
\label{effect.samplesize}
\end{figure}

A somewhat different question is how statistical power of studies changed over time. As an approximation, the total sample size of a study can be used. Figure \ref{median.samplesize.overtime} shows the median sample size of all studies of a given year. Again, to reduce the effects of distortion due to random fluctuation, only the medians for the years 1980 to 2017 are used ($n$ > 50,000).

@@

\end{knitrout}
\caption{Median sample size over time (years).}
\label{median.samplesize.overtime}
\end{figure}

\vspace{0mm}
There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results. In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = 1383)
The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3350).

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}

@@

The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes. This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.

@@

\end{knitrout}
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
\label{bias.results.cont.sep}
\end{figure}

@@

\end{knitrout}
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
\label{bias.results.bin.sep}
\end{figure}

Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses). The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}. The Figure suggests that the frequency of publication bias remains constant over time. The mean publication years have been restricted such that at least 180 meta-analyses are available per year such that random fluctuation is restricted to some extent. The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).

@@

\end{knitrout}
\caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
\label{pub.bias.overtime}
\end{figure}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Apr 16 13:55:01 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
 & Test Agreement & P-value Correlation \\ 
  \hline
egger.schwarzer & 0.88 & 0.38 \\ 
  egger.peter & 0.89 & 0.52 \\ 
  egger.rucker & 0.89 & 0.48 \\ 
  egger.harbord & 0.94 & 0.76 \\ 
  schwarzer.peter & 0.89 & 0.29 \\ 
  schwarzer.rucker & 0.88 & 0.34 \\ 
  schwarzer.harbord & 0.92 & 0.51 \\ 
  rucker.peter & 0.92 & 0.67 \\ 
  harbord.peter & 0.91 & 0.53 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)} 
\label{agreement.bin}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Apr 16 13:55:01 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
 & Test Agreement & P-value Correlation \\ 
  \hline
thomson.egger & 0.89 & 0.69 \\ 
  thomson.begg & 0.82 & 0.47 \\ 
  egger.begg & 0.79 & 0.36 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)} 
\label{agreement.cont}
\end{table}

\vspace{0mm}
Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies. The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}. %(Suggests that 10 is likely too small)
In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test. A s trend towards more rejections for larger sample sizes can be seen.

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-29-1}

\end{knitrout}
\caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
\label{pvalues.samplesize}
\end{figure}

\vspace{0mm}
One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects. The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.18. 
% A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes. In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses. 
In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes. In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-30-1}

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-31-1}

@@

\subsection{Small Study Effect Correction}
Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.

% # <<results = 'asis', Echo = FALSE>>=
% # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
% #                                             schwarzer.rejection = mean(schwarzer.test),
% #                                             rucker.rejection = mean(rucker.test),
% #                                             harbord.rejection = mean(harbord.test),
% #                                             peter.rejection = mean(peter.test))
% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
% # @

### 2019-04-17 report/chapter02.Rnw
Function update

PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH, 'code')
PATH_RESULTS = file.path(PATH, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

@@

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch02_fig',
               echo=TRUE, message=FALSE,
               fig.width=8, fig.height=3,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

>>>>

PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

@@

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch02_fig',
               echo=TRUE, message=FALSE,
               fig.width=8.1, fig.height=3,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@
